oREVIRT analysis

### 2022-11-04 analysis/irt_analysis.Rmd
work in Natalias comments
add models for selected items

```{r}
data <- read_csv("../data/clean_data.csv")

@@

@@

>>>>

```{r}
data <- read_csv("../data/clean_data.csv")
```

@@

## 1PL + guessing model

```{r}
prior_1pl_guess <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta")
```

```{r}
irt1_guess <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (1 | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_guess, "../saves/irt1_guess.rds")

irt1_guess <- readRDS("../saves/irt1_guess.rds")
```

@@

# IRT models for selected items

```{r}
frq_sel_items <- readRDS("../saves/selected_items.rds")

irt_dat_sel <- irt_dat%>%
  filter(targetWord %in% frq_sel_items)
```

```{r}
prior_1pl_sel <- 
  prior("normal(0, 2)", class = "Intercept") +
  prior("normal(0, 3)", class = "sd", group = "subjID") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord")
```

```{r}
irt1_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl_sel,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_sel, "../saves/irt1_sel.rds")

irt1_sel <- readRDS("../saves/irt1_sel.rds")
```

## 1PL + guessing model

```{r}
prior_1pl_guess <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta")
```

```{r}
irt1_guess_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (1 | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_guess_sel, "../saves/irt1_guess_sel.rds")

irt1_guess_sel <- readRDS("../saves/irt1_guess_sel.rds")
```

## 2PL + guessing model

```{r}
prior_va_3pl_sel <- 
  prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "b", nlpar = "logalpha") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") + 
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "targetWord", nlpar = "logalpha")
```

```{r}
irt3_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl_sel,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt3_sel, "../saves/irt3_sel.rds")

irt3_sel <- readRDS("../saves/irt3_sel.rds")
```

```{r}
loo_compare(irt1_guess_sel, irt3_sel)%>%as_tibble(rownames = "model")

brms::bayes_R2(irt3_sel)
```
